The GALEX View of ``Boyajian's Star''

### 2017-10-12 paper/paper.tex
a couple changes from Scott

Comparing co-added data from 2011 with a follow-up GALEX study of the \Kepler field in 2012, we find that KIC 8462852 faded by 3.5\%. This fading coincides with the slow variation reported by \citet{montet2016}, and is the first verification that this star is variable in the NUV.

>>>>

Comparing co-added data from 2011 with the follow-up GCK study of the \Kepler field in 2012, we find that KIC 8462852 faded by $3.5\pm1.0$\% in the NUV. This fading coincides with the slow variation reported by \citet{montet2016}, and is the first verification that this star is variable in the NUV. A preliminary examination of the typical variance between the GALEX and GCK data shows an average NUV change of 2.5\% for F-type stars. Thus we believe the NUV fading observed for KIC 8462852 is real, but not necessarily atypical at these wavelengths.
